Load `R2jags` and `ggmcmc`.

```{r}
require(R2jags, quietly=TRUE)
require(ggmcmc, quietly=TRUE)
```

Specify the model using JAGS syntax.
Write the model to a text file.

```{r}
cat("model
{
  for( i in 1 : n ) {
    z[i] ~ dnorm(0, 1)
    logit(pInt[i] ) <- alpha + beta + sigma * z[i]
    logit(pCntl[i]) <- alpha        + sigma * z[i]
    yInt[i]  ~ dbin(pInt[i] , nInt[i] )
    yCntl[i] ~ dbin(pCntl[i], nCntl[i])
  }
  alpha ~ dnorm(-5.0, 1.0E-1)
  beta  ~ dnorm(0.0, 1.0E-1)
  sigma ~ dnorm( 0.5, 1.0E-1) I(0, )
  # sigma ~ dgamma(0.001, 0.001)
}
",
file="modelMetaAnalysis.txt")
```

Prepare the data for JAGS.
`R2jags` requires the data object to be a list.

```{r}
D2 <- list(n=nrow(D), yInt=D$yInt, nInt=D$nInt, yCntl=D$yCntl, nCntl=D$nCntl)
```

Initialize the parameters.

```{r}
inits <- function() {list("alpha"=0, "beta"=0, "sigma"=0, "z"=rep(0, nrow(D)))}
```

Specify the parameters to track.

```{r}
params <- c("alpha", "beta", "sigma")
```

Set the random number seed.

```{r}
set.seed(as.numeric(as.Date("2014-08-27")))
```

Run the model.

```{r}
system.time(M <- jags(D2, inits, params, model.file="modelMetaAnalysis.txt", n.iter=250E3))
```

I can't figure out what's wrong with `jags.parallel`.
It returns this message,

> `Error in get(name, envir = envir) : invalid first argument`

```{r, eval=FALSE}
M <- jags.parallel(DJags, inits, params, model.file="modelMetaAnalysis.txt")
```

Convert the JAGS object to an MCMC object.
Also, convert the MCMC object to a ggs object.

```{r}
Mmcmc <- as.mcmc(M)
Mggs <- ggs(as.mcmc(M))
```

Check for convergence.

```{r mcmcConvergence}
ggs_traceplot(Mggs)
ggs_autocorrelation(Mggs)
ggs_compare_partial(Mggs)
```

**Convergence looks good.**
So, show the model output.

```{r mcmcPosterior}
M
ggs_density(Mggs)
```

Combine the MCMC chains.
Calculate some useful output from the model.

```{r}
Mdf <- rbind(data.frame(chain = 1, Mmcmc[[1]]),
             data.frame(chain = 2, Mmcmc[[2]]),
             data.frame(chain = 3, Mmcmc[[3]]))
scale <- 10000
Mdf$predInt <- exp(Mdf$alpha + Mdf$beta) / (1 + exp(Mdf$alpha + Mdf$beta))
Mdf$predCntl <- exp(Mdf$alpha) / (1 + exp(Mdf$alpha))
Mdf$rateInt <- Mdf$predInt * scale
Mdf$rateCntl <- Mdf$predCntl * scale
Mdf$rateDiff <- Mdf$rateInt - Mdf$rateCntl
```

Summarize.

```{r mcmcOutput}
Mgg <- melt(Mdf, id.vars=c("chain"), measure.vars=c("rateInt", "rateCntl", "rateDiff"), value.name="rate")
Mgg$varLabel <- factor(Mgg$variable, labels=c("Intervention", "Control", "Difference"))
ggplot(Mgg[Mgg$varLabel %in% c("Intervention", "Control"), ], aes(x=rate, fill=varLabel)) +
  geom_density(alpha=1/2) +
  scale_x_continuous("Rate per 10,000") +
  scale_y_continuous("Density") +
  scale_fill_discrete("")
ggplot(Mgg[Mgg$varLabel == "Difference", ], aes(x=rate)) +
  geom_density(alpha=1/2) +
  scale_x_continuous("Rate difference per 10,000") +
  scale_y_continuous("Density") +
  geom_vline(xIntercept = 0)
```

Save the JAGS objects.

```{r}
modelJAGS <- list(metadata = list(timestamp = Sys.time(),
                                  R = R.version.string,
                                  R2jags = packageVersion("R2jags")),
                  jags = M,
                  chains = Mdf)
save(modelJAGS, file="modelJAGS.RData")
```
