# Read Ahles

Read data from 
[Ahles TA, et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2988635/)
"Longitudinal Assessment of Cognitive Changes Associated With Adjuvant Treatment for Breast Cancer: Impact of Age and Cognitive Reserve."
*J Clin Oncol.* 
2010 Oct 10; 28(29): 4434-4440.

Data file was requested and received from the co-author, [Yuelin Li](https://www.mskcc.org/profile/yuelin-li), in October 2015.

Read data file (text format).

```{r}
path <- "StudyDocuments/CognitiveImpairment"
# list.files(path)
f <- sprintf("%s/%s", path, "Soulsby_means.txt")
D <- fread(f, sep="|")
```

Study design.

```{r}
D[, .(nrows = .N, totalN = sum(N)), .(txgrp, ptime)]
```

Instruments.

```{r}
D[, .N, .(Variable, Label)]
```

Save working data tables to file if the integrity checks passed.
I don't need to save `DOno` since the integrity checks passed.

```{r}
metadata = makeMetadata(D)
f <- "Ahles.RData"
save(D, metadata, file=f)
message(sprintf("%s saved on: %s\nFile size: %s bytes", 
                f,
                file.mtime(f),
                file.size(f)))
```
