# Replicate Ono

Replicate data from 
[Ono, Miyuki, et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4354286/)
"A Meta-Analysis of Cognitive Impairment and Decline Associated with Adjuvant Chemotherapy in Women with Breast Cancer."
*Front Oncol.* 
2015; 5: 59. 

Data file was requested and received from the co-author, [James Ogilvie](https://www.griffith.edu.au/health/school-applied-psychology/rhd-students/james-ogilvie), in October 2015.

Read data file (Google Sheet format).

```{r}
# path <- "StudyDocuments/CognitiveImpairment"
# list.files(path)
# f <- sprintf("%s/%s", path, "Requested Chemo Data.xlsx")
url <- "https://docs.google.com/spreadsheets/d/1kANi0laOaoFbBXxbanARcp7zowQ5eOfOcOr_sQLhJHo/edit?usp=sharing"
gs_auth()
gs_url(url)
# D0 <- read.xlsx(f, sheet=1)
D0 <- gs_read(gs_url(url))
D0 <- data.table(D0)
```

Show a map of the column names and locations.

```{r}
colNames <- data.frame(colNum = 1:ncol(D0),
                       colCell = c(LETTERS,
                                   sprintf("%s%s", LETTERS[1], LETTERS),
                                   sprintf("%s%s", LETTERS[2], LETTERS),
                                   sprintf("%s%s", LETTERS[3], LETTERS))[1:ncol(D0)],
                       varName = names(D0))
colNames
```

Put the summary rows in a separate data table, `DOno`.

```{r}
DOno <- D0[is.na(First.Auth), c(51:ncol(D0)), with=FALSE]
```

Put the instrument-level rows in a separate data table, `D`.
Only keep the columns needed to calculate fixed and random effects statistics.

**Need more information** on the `RANDOM.EFFECT` column.
This column has a mean of `r D0[, mean(RANDOM.EFFECT, na.rm=TRUE)]` 
and a standard deviation of `r D0[, sd(RANDOM.EFFECT, na.rm=TRUE)]`.
It's a mystery where this comes from.

```{r}
importantVar <- c(1, 7:10, 12:15, 17, 34:38, 64, 31:33)
D <- D0[!is.na(First.Auth), importantVar, with=FALSE]
setnames(D,
         names(D),
         c("author",
           "comparisonGroup",
           "healthyGroup",
           "treatmentGroup",
           "timeDays",
           "nGroup1",
           "nGroup2",
           "nTotal",
           "ageGroup1",
           "ageGroup2",
           "meanGroup1",
           "sdGroup1",
           "meanGroup2",
           "sdGroup2",
           "direction",
           "randomEffect",
           gsub("\\.", "", names(D0)[31:33])))  # NEED TO FIND OUT WHERE RANDOM EFFECT COMES FROM
D <- D[direction == "Lower worse",
       `:=` (diffMean = meanGroup2 - meanGroup1)]
D <- D[direction == "Greater worse",
       `:=` (diffMean = meanGroup1 - meanGroup2)]
D <- D[,
       `:=` (sdPooled = sqrt((((nGroup1 - 1) * (sdGroup1 ^ 2)) +
                                ((nGroup2 - 1) * (sdGroup2 ^ 2))) /
                               (nGroup1 + nGroup2 - 2)))]
D <- D[,
       `:=` (cohenD = diffMean / sdPooled)]
D <- D[,
       `:=` (hedgesG = cohenD * (1 - (3 / ((4 * nTotal) - 9))))]
D <- D[,
       `:=` (var1 = (nGroup1 + nGroup2) / (nGroup1 * nGroup2),
             var2 = hedgesG ^ 2 / (2 * (nGroup1 + nGroup2)))]
D <- D[,
       `:=` (variance = var1 + var2)]
D <- D[,
       `:=` (se = sqrt(variance),
             weightFE = 1 / variance)]
D <- D[,
       `:=` (effSizeWeightedFE = weightFE * hedgesG)]
D <- D[, weightRE := 1 / (variance + randomEffect)]
D <- D[, effSizeWeightedRE := weightRE * hedgesG]
```

Domains and tests.

```{r}
D[, .N, .(CognitiveDomainPrimary, CogTest)][order(CognitiveDomainPrimary, CogTest)]
```

Calculate fixed effects statisitcs.

```{r}
DFixed <- D[,
              .(df = .N,
                sumWeights = sum(weightFE),
                effSize = sum(effSizeWeightedFE) / sum(weightFE),
                se = sqrt(1 / sum(weightFE)),
                sumEffSizeWeighted = sum(effSizeWeightedFE),
                ssEffSizeWeighted = sum(weightFE * hedgesG ^ 2),
                ssWeights = sum(weightFE ^ 2)),
              .(author, timeDays)]
DFixed <- DFixed[,
                 `:=` (z = effSize / se,
                       lowerCI = effSize + qnorm(0.025) * se,
                       upperCI = effSize + qnorm(0.975) * se,
                       Q = ssEffSizeWeighted - (sumEffSizeWeighted ^ 2 / sumWeights),
                       criticalValue = qchisq(0.05, df, lower.tail=FALSE))]
DFixed <- DFixed[,
                 `:=` (pvalue = pchisq(Q, df, lower.tail=FALSE),
                       Isq = 100 * ((Q - df) / Q))]
```

Check if my calculations agree with Ono's.

```{r, results="asis"}
isCheckFixedPassed <- all.equal(DOno[, .(StudyES, z, Q)], 
                                DFixed[, .(effSize, z, Q)],
                                check.names=FALSE)
message(sprintf("Do my FIXED effect statistic calculations agree with Ono's? %s",
                isCheckFixedPassed))
print(xtable(DFixed), type="html")
```

Calculate random effects statisitcs.

```{r}
DRandom <- D[,
             .(df = .N,
               sumWeights = sum(weightRE),
               ssEffSizeWeighted = sum(weightRE * hedgesG ^ 2),
               ssWeights = sum(weightRE ^ 2),
               sumEffSizeWeighted = sum(effSizeWeightedRE),
               effSize = sum(effSizeWeightedRE) / sum(weightRE),
               se = sqrt(1 / sum(weightRE))),
             .(author, timeDays)]
DRandom <- DRandom[,
                   `:=` (z = effSize / se,
                         lowerCI = effSize + qnorm(0.025) * se,
                         upperCI = effSize + qnorm(0.975) * se,
                         Q = ssEffSizeWeighted - (sumEffSizeWeighted ^ 2 / sumWeights),
                         criticalValue = qchisq(0.05, df, lower.tail=FALSE))]
DRandom <- DRandom[,
                   `:=` (pvalue = pchisq(Q, df, lower.tail=FALSE),
                         Isq = 100 * ((Q - df) / Q))]
```

Check if my calculations agree with Ono's.

```{r, results="asis"}
isCheckRandomPassed <- all.equal(DOno[, c(19, 21, 24), with=FALSE], 
                                 DRandom[, .(effSize, z, Q)],
                                 check.names=FALSE)
message(sprintf("Do my RANDOM effect statistic calculations agree with Ono's? %s",
                isCheckRandomPassed))
print(xtable(DRandom), type="html")
```

Save working data tables to file if the integrity checks passed.
I don't need to save `DOno` since the integrity checks passed.

```{r}
metadataD = makeMetadata(D)
metadataDFixed = makeMetadata(DFixed)
metadataDRandom = makeMetadata(DRandom)
if (isCheckFixedPassed & isCheckRandomPassed) {
  f <- "Ono.RData"
  save(D,
       metadataD,
       DFixed,
       metadataDFixed,
       DRandom,
       metadataDRandom,
       file=f)
  message(sprintf("%s saved on: %s\nFile size: %s bytes", 
                  f,
                  file.mtime(f),
                  file.size(f)))
} else {
  warning(sprinf("Integrity checks failed.\n%s not saved.", f))
}
```
